\paperTitle

### 2014-05-18 doc/icml2014/background.tex
more change

Finally, we assume the graphical model is in a canonical form
in which all observed variables are leaves:
\begin{assumption}[Canonical form]
  \label{asm:canonical}
  For each observed variable $x_v$, there exists exactly one $\sC \in \sG$
  such that $\sC = \{ x_v, h_{i} \}$ for some hidden node $h_{i}$.
\end{assumption}
The following lemma shows that this is not a real assumption (see the appendix for the proof):
\begin{lemma}[Reduction to canonical form]
\label{lem:reduction}
Every graphical model can be transformed into canonical
form (via \figureref{reduction}).
There is a one-to-one correspondence between the parameters of the transformed
and original models.
\end{lemma}

@@

% No parameters yet
The tensor factorization method attacks the heart of the non-convexity
  in latent-variable models, providing some information about the hidden variables
  in the form of the conditional moments $\mOpp{v}{i} = \Pr(x_v \mid h_i)$.
  Note that $\TensorFactorize$ only examines the conditional independence structure
  of the graphical model, not its parametrization.
  If $i$ is the single parent of $v$ (e.g., $\Pr(x_1^a \mid h_1)$ in \figureref{approach}),
  then this conditional moment is a parameter of the model,
  but this is in general not the case (e.g., $\Pr(x_2^a \mid h_1)$).
  Furthermore, there are other parameters (e.g., $\Pr(h_4 \mid h_2, h_3)$) which we do
  not have a handle on yet.
  In general, there is a gap between the conditional moments
  and the model parameters,
  something we will address in the next two sections.

>>>>

Finally, we assume the graphical model is in a canonical form
in which all observed variables are leaves:
\begin{assumption}[Canonical form]
  \label{asm:canonical}
  For each observed variable $x_v$, there exists exactly one $\sC \in \sG$
  such that $\sC = \{ x_v, h_{i} \}$ for some hidden node $h_{i}$.
\end{assumption}
The following lemma shows that this is not a real assumption (see the appendix for the proof):
\begin{lemma}[Reduction to canonical form]
\label{lem:reduction}
Every graphical model can be transformed into canonical
form. % (via \figureref{reduction}).
There is a one-to-one correspondence between the parameters of the transformed
and original models.
\end{lemma}

@@

The tensor factorization method attacks the heart of the non-convexity
  in latent-variable models, providing some information about the hidden variables
  in the form of the conditional moments $\mOpp{v}{i} = \Pr(x_v \mid h_i)$.
  Note that $\TensorFactorize$ only examines the conditional independence structure
  of the graphical model, not its parametrization.

% No parameters yet
  If $i$ is the single parent of $v$ (e.g., $\Pr(x_1^a \mid h_1)$ in \figureref{approach}),
  then this conditional moment is a parameter of the model,
  but this is in general not the case (e.g., $\Pr(x_2^a \mid h_1)$).
  Furthermore, there are other parameters (e.g., $\Pr(h_4 \mid h_2, h_3)$) which we do
  not have a handle on yet.
  In general, there is a gap between the conditional moments
  and the model parameters,
  which we will address in the next two sections.

### 2014-05-18 doc/icml2014/undirected.tex
more change

Note that our pseudolikelihood-based approach
does depend exponentially on the size of the sub-neighborhoods,
which could be larger than the largest clique size.
Therefore,
for this approach to be effective,
each node essentially should have low degree or locally exhibit a lot of
conditional independence.
%While this method is only viable for graphs with small sub-neighboof low
%degree, i.e.\@ when $|\sN(a)|$ is small,
On the positive side, we can handle graphical models with high treewidth;
neither sample nor computational complexity necessarily depends on the treewidth.
%For example, for an $n \times n$ grid model, the treewidth is $n$,
%but it is the degree (only 4 in this case) that governs the computational complexity.
For example, an $n\times n$ grid model has a treewidth of $n$, but each
  clique is of size at most $2$ and the degree is at most $4$.

>>>>

Note that our pseudolikelihood-based approach
does depend exponentially on the size of the sub-neighborhoods,
which could be exceed the largest clique size.
Therefore,
%for our approach to be effective,
each node essentially should have low degree or locally exhibit a lot of
conditional independence.
%While this method is only viable for graphs with small sub-neighboof low
%degree, i.e.\@ when $|\sN(a)|$ is small,
On the positive side, we can handle graphical models with high treewidth;
neither sample nor computational complexity necessarily depends on the treewidth.
%For example, for an $n \times n$ grid model, the treewidth is $n$,
%but it is the degree (only 4 in this case) that governs the computational complexity.
For example, an $n\times n$ grid model has a treewidth of $n$, but the degree is at most $4$.
